---
title: "Fig2_code"
author: "Xueqi"
date: "2025-05-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup}
rm(list=ls()) 
library(readxl)
library(xlsx)
library(plyr)
library(dplyr)
library(tidyverse)
library(writexl)
library(reshape)
library(ggpubr)
library(ggplot2)
library(ggrepel)
library(ggridges)
library(ggforce)
library(reshape2)
library(ggbump)
library(ggbreak)

wd <- "./"
setwd(wd)

xytitle <- 8
textsize <- 8
anglenum <- 0 
vj <- 0 
hj <- 0.5 
legendsize <- 0.4
legendposit <- ''
titlesize <- 9
```

# Figure 2A. Geographic distribution of participants across provinces.
```{r A}

data <- as.data.frame(read_excel('BirthCohortData.xlsx',sheet=1))
df <- data[,c("Province","distribute")]
df2 <- df %>% 
  dplyr::group_by(Province) %>% 
  dplyr::summarise(value = n()/length(na.omit(df$Province))) %>%
  dplyr::ungroup() 

df2$Province <- factor(df2$Province,level=c("Sichuan","Gansu","Chongqing","Guizhou","Qinghai"))

new_values <- sapply(1:length(df2$value), function(i) {
  if (i == 1) {
    return(df2$value[length(df2$value)] / 2)  
  } else {
    return(((sum(df2$value[length(df2$value):(8-i)])) + (df2$value[7-i]) / 2)) 
  }
})

label <- c("Sichuan","Gansu","Chongqing","Guizhou","Qinghai")
col <- c("Gansu" = "#439EB7", "Qinghai" = "#E28B55", "Guizhou" = "#DCB64D", "Sichuan" = "#4CA198", "Chongqing" = "#835B82")

ggplot(data = df2, mapping = aes(x = 'Content', y = value, fill = Province)) + 
  geom_col(color='white') +
  geom_text(aes(label = label),  size = 2.7,
            position = position_identity(),
            x = c(1.2, 1.2, 1.2, 1.2, 1.2),
            y = new_values
  )+
  coord_polar("y", start=0)+
  labs(x = '', y = '', title = '')+
  scale_fill_manual(values=col,name='')+
  theme(
    axis.title.x = element_blank(), axis.title.y = element_blank(),  axis.text.x = element_blank(),   
    axis.text.y = element_blank(), panel.border = element_blank(),panel.grid=element_blank(),
    axis.ticks = element_blank(),plot.margin = unit(c(0, 0, 0, 0), "cm")  )+
  theme(     
    panel.grid.major = element_blank( ),
    panel.grid.minor = element_blank( ),
    panel.border = element_blank( ),
    axis.title.y = element_blank(),  
    axis.text.y = element_blank(),   
    axis.ticks.x = element_blank(), 
    axis.ticks.y = element_blank(), 
    panel.background = element_rect(fill=NA, colour=NA),
    legend.background = element_rect(fill=NA, colour=NA),
    legend.position = 'right', 
    legend.title = element_text(size = textsize),
    legend.key.size = unit(legendsize, "cm"),  
    legend.text = element_text(size = textsize),
    panel.background = element_rect(fill=NA, colour=NA)
  )

ggsave(paste0('F2A-2',".pdf"),width =7, height = 6, units = "cm")

```

# Figure 2B. Monthly enrollment of participants.
```{r B}
data <- read.delim(paste0("Enrollment dataset.txt"),
           sep = "\t",
           header = T,
           fill = TRUE)
colnames(data)

df <- data %>% 
  dplyr::group_by(Month) %>% 
  dplyr::summarise(value = sum(Number.of.enrolled.participants)) %>%
  dplyr::ungroup() %>% 
  dplyr::mutate(cumulative_value = cumsum(value),
                group1=1)  

ggplot() +
  geom_segment(data = df,
               aes(x = Month, y = value, xend = Month, yend = 0),
               size = 1.5, colour = c("#416997"),alpha = 1) +
  geom_area(data = df, aes(x = Month, y = cumulative_value/20,group=group1), fill=c("#324856"),alpha = 0.4,size=0.1) + 
  scale_y_continuous(name = expression("Number of participants"),
                     sec.axis = sec_axis(~ (. + 0)*20, 
                                         name = "Total number of participants", 
                                         breaks = seq(0, 16000, 4000)),
                     limits = c(0, 800),
                     expand = c(0, 0)) +
  theme(axis.title.x = element_text(size=xytitle,face='bold'),
        axis.text.x = element_text( size = textsize, angle = 90,hjust = 1, vjust = 0.5 ),
        axis.title.y = element_text(size=xytitle,face='bold'),
        axis.text.y = element_text( size = 7, angle = 90,vjust = 0,hjust= 0.5),
        plot.title = element_text(size = titlesize),          
        plot.subtitle = element_text(size = textsize),       
        panel.grid.major = element_blank( ),
        panel.grid.minor = element_blank( ),
        panel.border = element_blank( ),
        panel.background = element_rect(fill=NA, colour=NA),
        legend.background = element_rect(fill=NA, colour=NA),
        legend.title = element_text( size = textsize),
        legend.text = element_text( size = textsize),
        legend.key.size =  unit(0.5, "cm"),
        
        axis.line = element_line(colour = "black", size = 0.25, 
                                 arrow = arrow(type = "closed", 
                                               angle = 12,
                                               length = unit(0.2, "cm"))
        ),                 
        axis.ticks = element_line(colour = "black", size = 0.25),
        axis.ticks.length.x=unit(0.08, "cm"),
        axis.ticks.length.y=unit(0.08, "cm"),
        
  )
  
ggsave(paste0('F2B',".pdf"),width =10, height = 8, units = "cm")

```

# Figure 2C. Distribution of altitudes for participants from different provinces.
```{r C}
data <- as.data.frame(read_excel('BirthCohortData.xlsx',sheet=1))

df<-data[,c("Province","Altitude")]
df$Province<-factor(df$Province,levels = c("Sichuan","Gansu","Chongqing","Guizhou","Qinghai"))

df <- df %>% 
  dplyr::mutate(gap = cut(Altitude,
                          breaks = seq(0, max(df$Altitude, na.rm = TRUE) + 100, by = 100),  
                          labels = seq(100, max(df$Altitude, na.rm = TRUE) + 100, by = 100),  
                          right = FALSE))

pre_result<-df %>% dplyr::group_by(Province, gap) %>%
  dplyr::summarise(value = n()) %>%
  dplyr::ungroup()

pre_result$gap <- as.numeric(pre_result$gap)*100

col <- c("Gansu" = "#439EB7", "Qinghai" = "#E28B55", "Guizhou" = "#DCB64D", "Sichuan" = "#4CA198", "Chongqing" = "#835B82")

ggplot(pre_result, aes(x = gap, y = value,color=Province, fill = Province, group = Province)) + 
  geom_area(aes(fill = Province),size=0.1) + 
  scale_y_continuous(limits = c(0, 4500), expand = c(0, 0),  breaks = c(0,1500,3000,4500)) +
  scale_x_continuous(limits = c(0, 4500), expand = c(0, 0),  breaks = c(0,1500,3000,4500)) +
  scale_fill_manual(values = col)+
  scale_color_manual(values = col)+
  theme_classic()+
  xlab("Altitude")+
  ylab("Frequency")+
  theme(
    axis.title.x = element_text(size = xytitle, face = 'bold'),
    axis.text.x = element_text(size = textsize, angle = anglenum, vjust = vj, hjust = hj),
    axis.title.y = element_text(size = xytitle, face = 'bold'),
    axis.text.y = element_text( size = 7, angle = 90,vjust = 0,hjust= 0.5),
    plot.title = element_text(size = titlesize),
    plot.subtitle = element_text(size = textsize),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_rect(fill = NA, colour = NA),
    legend.background = element_rect(fill = NA, colour = NA),

    axis.line.x = element_line(
      colour = "black",
      size = 0.25
    ),
    axis.line.y = element_line(
      colour = "black",
      size = 0.25
    ),
    axis.ticks = element_line(colour = "black", size = 0.25),
    axis.ticks.length.x = unit(0.08, "cm"),
    axis.ticks.length.y = unit(0.08, "cm"),
    legend.position = 'top', 
    legend.title = element_text(size = textsize),
    legend.key.size = unit(legendsize, "cm"),  
    legend.text = element_text(size = textsize)
  )
  

ggsave(paste0('F2C',".pdf"),width =7, height = 6, units = "cm")

```

# Figure 2D. A pie chart showing the proportions of Han and ethnic minority participants.
```{r D}


data <- data.frame(Ethnicity = c("Han", "Minorities", "Unknown"),  percentage = c(0.764,0.193,0.043),
                   focus=c(0,0.2,0))
data$Ethnicity<-factor(data$Ethnicity,levels = c("Han","Minorities","Unknown"))

data2 <- data %>%
  dplyr::arrange(Ethnicity) %>% 
  dplyr::mutate(
    cumulative = cumsum(percentage),         
    start = lag(cumulative, default = 0),   
    mid = (start + cumulative) / 2,           
    angle = mid * 2 * pi,
    label_x = 1.5 * cos(angle),
    label_y = 1.5 * sin(angle)
  )

data2[1,1] <- 'Minorities'
data2[2,1] <- 'Han'
data2[3,1] <- 'Unknown'

ggplot()+  
  geom_arc_bar(data=data,
               stat = "pie",              
               aes(x0=0,y0=0,r0=0,r=2, 
                   amount=percentage,                   
                   fill=Ethnicity,color=Ethnicity,                   
                   explode=focus),    
               show.legend = F)+
  scale_fill_manual(values = c("#B19C7D","#7F5F52","#B27D49"))+
  scale_color_manual(values = c("white","white","white"))+
  labs(x="",y="")+
  theme(panel.grid=element_blank(),
        panel.background=element_blank(),
        axis.text=element_blank(),
        axis.title = element_blank(),
        axis.ticks =element_blank(),
        axis.line = element_blank(),
        legend.text =  element_text(size=7,color="black"))+
  geom_text(data = data2, aes(x = label_x, y = label_y, label = Ethnicity), 
            color = "black", size = 4)

ggsave(paste0('F2D',".pdf"),width =6, height = 6, units = "cm")
```
# Figure 2E. The top ten ethnic minority groups in WCBC. 
```{r E}
data <- as.data.frame(read_excel('BirthCohortData.xlsx',sheet=1))

df<-data[,c("Province","Ethnicity")]
df$Ethnicity[which(is.na(df$Ethnicity))]="Unknown"
df<-df[-which(df$Ethnicity=="Han"|df$Ethnicity=="Unknown"),]

df<-as.data.frame(table(df))
pre_result<-df
pre_result$Province<-factor(pre_result$Province,levels = c("Sichuan","Gansu","Chongqing","Guizhou","Qinghai"))

pre_result$Freq<-log2(pre_result$Freq+1)

col <- c("Gansu" = "#439EB7", "Qinghai" = "#E28B55", "Guizhou" = "#DCB64D", "Sichuan" = "#4CA198", "Chongqing" = "#835B82")
pre_result

pre_result_sorted <- pre_result %>% 
  group_by(Ethnicity) %>%  
  dplyr::summarise(total_Freq = sum(Freq)) %>%  
  dplyr::arrange(desc(total_Freq)) %>%  
  dplyr::top_n(10, total_Freq) %>%  
  dplyr::left_join(pre_result, by = "Ethnicity") %>%  
  dplyr::mutate(Ethnicity = factor(Ethnicity, levels = unique(Ethnicity)))

pre_result <- pre_result %>% 
  dplyr::filter(Ethnicity %in% unique(pre_result_sorted$Ethnicity)) %>% 
  dplyr::mutate(Ethnicity = factor(Ethnicity, levels = unique(Ethnicity)))  

ggplot(pre_result, aes(x = reorder(Ethnicity,-Freq), y = Freq, fill = Province)) +
  geom_bar(stat = "identity", width = 0.7,color='white') +  
  scale_fill_manual(values =col)+
  labs(x = "",y='') +
  scale_y_continuous(limits = c(0, 30), expand = c(0, 0), breaks = round(seq(0,30,5), digits = 1)) +
  theme(axis.title.x = element_text(size=xytitle,face='bold'),
        axis.title.y = element_text(size=xytitle,face='bold'),
        axis.text.x = element_text( size = textsize, angle = 30, vjust = 0.8,hjust= 0.7 ),
        plot.title = element_text(size = titlesize),          
        plot.subtitle = element_text(size = textsize),       
        panel.grid.major = element_blank( ),
        panel.grid.minor = element_blank( ),
        panel.border = element_blank( ),
        
        panel.background = element_rect(fill=NA, colour=NA),
        legend.background = element_rect(fill=NA, colour=NA),
        
        axis.line.x = element_line(colour = "black",size = 0.25),
        axis.line.y = element_line(colour = "black",size = 0.25),
        axis.ticks = element_line(colour = "black", size = 0.25),
        axis.ticks.length.x=unit(0.08, "cm"),
        axis.ticks.length.y=unit(0.08, "cm"),
        legend.position = 'none', 
        legend.title = element_text(size = textsize),
        legend.key.size = unit(legendsize, "cm"),  
        legend.text = element_text(size = textsize)  )
  
  

ggsave(paste0('F2E',".pdf"),pe,width =8, height = 6.5, units = "cm")
```

# Figure 2F. Distribution of pregnant age of participants from different provinces. The dashed line represents the average age of pregnant women in each province. 
```{r F}
data <- as.data.frame(read_excel('BirthCohortData.xlsx',sheet=1))
myda <- data
myda$Type_3<-factor(myda$Province,levels =c("Qinghai","Guizhou","Chongqing","Gansu","Sichuan"), ordered=T)
medians <- myda %>% 
  dplyr::group_by(Type_3) %>% 
  dplyr::summarize(median_length = mean(age, na.rm = TRUE),
                   ymin = min(Type_3),
                   ymax = max(Type_3))

ggplot(myda, aes(x = age, y = Type_3, color=Type_3,fill = Type_3)) + 
  geom_density_ridges(quantile_lines = TRUE, 
                      quantiles = c(0.025, 0.975), 
                      alpha = 1, 
                      linetype = "solid",  
                      jittered_points = FALSE,
                      size = 0.2) +
  geom_segment(data = medians, 
               aes(x = median_length, 
                   xend = median_length, 
                   y = as.numeric(factor(Type_3)) - 0, 
                   yend = as.numeric(factor(Type_3)) + 1.5, 
                   color = 'black'
               ), 
               linetype = "dashed", 
               size = 0.5) + 
  scale_fill_manual(values=col)+
  scale_color_manual(values=col)+
  scale_y_discrete( expand = c(0, 0))+
  xlab("Age") + ylab("") +
  theme(axis.title.x = element_text(size=xytitle,face='bold'),
        axis.title.y = element_text(size=xytitle,face='bold'),
        axis.text.x = element_text( size = textsize, angle = 0, vjust = 0.5,hjust= 0.5 ),
        plot.title = element_text(size = titlesize),          
        plot.subtitle = element_text(size = textsize),       
        panel.grid.major = element_blank( ),
        panel.grid.minor = element_blank( ),
        panel.border = element_blank( ),
        
        panel.background = element_rect(fill=NA, colour=NA),
        legend.background = element_rect(fill=NA, colour=NA),
        
        axis.line.x = element_line(colour = "black",size = 0.25),
        axis.line.y = element_line(colour = "black",size = 0.25),
        axis.ticks = element_line(colour = "black", size = 0.25),
        axis.ticks.length.x=unit(0.08, "cm"),
        axis.ticks.length.y=unit(0.08, "cm"),
        legend.position = 'none', 
        legend.title = element_text(size = textsize),
        legend.key.size = unit(legendsize, "cm"),  
        legend.text = element_text(size = textsize)  )


ggsave(paste0('F2F',".pdf"),pg,width =9, height = 6, units = "cm")
```

# Figure 2G. Proportions of participants who reached each follow-up visit. 
```{r G}
data <- as.data.frame(read_excel('BirthCohortData.xlsx',sheet=1))

df <- data[,c("Province","distribute")]
df2 <- df %>% 
  dplyr::filter(!is.na(distribute) ) %>% 
  dplyr::group_by(distribute) %>% 
  dplyr::summarise(value = n()/length(na.omit(df$distribute))) %>%
  dplyr::ungroup() 

df2$distribute <- factor(df2$distribute,level=c("Early pregnancy" ,"Late pregnancy","Delivery", "1-month","6-months","1-year","2-years","3-years"))
df2 <- df2 %>% dplyr::arrange(distribute)

new_values <- sapply(1:length(df2$value), function(i) {
  if (i == 1) {
    return(df2$value[length(df2$value)] / 2)  
  } else {
    return(((sum(df2$value[length(df2$value):(10-i)])) + (df2$value[9-i]) / 2)) 
  }
})
label <- c("3-years","2-years","1-year","6-months","1-month","Delivery","Late pregnancy", "Early pregnancy" )
col2 <- c("Early pregnancy"='#BCE4D8FF',"Late pregnancy"= '#46A1B8FF', "Delivery"='#2C5985FF', 
          "1-month"='#E1A663FF',"6-months"= '#CF9363FF',"1-year"= '#BF8061FF', "2-years"='#BB6A4FFF', "3-years"='#BB5137FF')

ggplot(data = df2, mapping = aes(x = 'Content', y = value, fill = distribute)) + 
  geom_col(color='white') +
  coord_polar("y", start=0)+
  labs(x = '', y = '', title = '')+
  scale_fill_manual(values=col2,name='')+
  theme(
    axis.title.x = element_blank(), axis.title.y = element_blank(),  axis.text.x = element_blank(),   
    axis.text.y = element_blank(), panel.border = element_blank(),panel.grid=element_blank(),
    axis.ticks = element_blank(),plot.margin = unit(c(0, 0, 0, 0), "cm")  )+themenoback+themelegendright

ggsave(paste0('F2G.pdf'),pf,width =7, height = 6, units = "cm")
```

# Figure 2H. Numbers of participants who completed each follow-up visit.
```{r H}
data <- as.data.frame(read_excel('BirthCohortData.xlsx',sheet=1))

p <- list()
p1 <- list()

for (i in c( "Sichuan","Gansu","Chongqing","Guizhou","Qinghai")) { 
  
  data2 <- dplyr::filter(data,province==i)
  pre <- data2[,c(3,4,5,6)] %>% melt()
  pre_result <- pre %>%
    dplyr::filter(!is.na(value)) %>%
  dplyr::group_by(province, value) %>%
    dplyr::summarise(num = n()) %>%
    dplyr::ungroup()
  
  col <- c("Gansu" = "#439EB7", "Qinghai" = "#E28B55", "Guizhou" = "#DCB64D", "Sichuan" = "#4CA198", "Chongqing" = "#835B82")
  
  x_ticks <- c(4, 12, 28, 40)

  p1[[i]] <- ggplot(pre_result, aes(x = value, y = num, color=province,fill = province, group = province)) + 
    geom_area(aes(fill = province), alpha = 1,size=0.1) + 
    scale_y_continuous(limits = c(0, 1200), breaks = seq(0, 1200, 400), expand = c(0, 0)) + 
    scale_x_continuous(limits = c(0, 44),breaks = seq(0, 44, 10), expand = c(0, 0)) + 
    labs(y = i, color = '', x = '') + 
    scale_fill_manual(values = col) +
    scale_color_manual(values = col) +  
    theme(
      axis.title.x = element_text(size = xytitle, face = 'bold'),
      axis.text.x = element_text(size = textsize, angle = anglenum, vjust = vj, hjust = hj),
      axis.title.y = element_text(size = xytitle, face = 'bold'),
      axis.text.y = element_text(size = textsize),
      plot.title = element_text(size = titlesize),
      plot.subtitle = element_text(size = textsize),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      panel.background = element_rect(fill = NA, colour = NA),
      legend.background = element_rect(fill = NA, colour = NA),
      
      axis.line.x = element_line( colour = "black",size = 0.25),
      axis.line.y = element_line(colour = "black",size = 0.25),
      axis.ticks = element_line(colour = "black", size = 0.25),
      axis.ticks.length.x = unit(0.08, "cm"),
      axis.ticks.length.y = unit(0.08, "cm"),
      legend.position = 'none', 
      legend.title = element_text(size = textsize),
      legend.key.size = unit(legendsize, "cm"),  
      legend.text = element_text(size = textsize)    ) 
  
  child <- data2[,c(3,7,8,9,10,11)]
  colnames(child) <- c("province","1-month","6-months","1-year", "2-years" , "3-years" )
  child2 <- child %>%
    pivot_longer(cols = -province, names_to = "col", values_to = "value") %>%
    dplyr::group_by(province, col) %>%
    dplyr::summarise(freq = sum(value == 1, na.rm = TRUE)) %>%
    dplyr::ungroup()
  
  child2$freq <- as.numeric(child2$freq)
  col <- c("Gansu" = "#439EB7", "Qinghai" = "#E28B55", "Guizhou" = "#DCB64D", "Sichuan" = "#4CA198", "Chongqing" = "#835B82")
  child2$col <- factor(child2$col, levels = c("1-month","6-months","1-year", "2-years" , "3-years" ))
  col2 <- c( "1-month"='#E1A663FF',"6-months"= '#CF9363FF',"1-year"= '#BF8061FF', "2-years"='#BB6A4FFF', "3-years"='#BB5137FF')
  p[[i]] <- ggplot(child2, aes(x = freq, y = col,fill = col)) + 
    geom_bar(stat="identity", color = "white",width = 0.7,alpha=1,size=0.3) +
    scale_x_continuous(limits=c(0,4500), breaks=seq(0,4500,1500), expand = c(0,0))+ 
    labs(y='',color='',x='')+
    scale_colour_manual(values = col) +  
    scale_fill_manual(values = col2) + 
    theme(
      axis.title.x = element_text(size = xytitle, face = 'bold'),
      axis.text.x = element_text(size = textsize, angle = anglenum, vjust = vj, hjust = hj),
      axis.title.y = element_text(size = xytitle, face = 'bold'),
      axis.text.y = element_text(size = textsize),
      plot.title = element_text(size = titlesize),
      plot.subtitle = element_text(size = textsize),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      panel.background = element_rect(fill = NA, colour = NA),
      legend.background = element_rect(fill = NA, colour = NA),
      
      axis.line.x = element_line( colour = "black",size = 0.25),
      axis.line.y = element_line(colour = "black",size = 0.25),
      axis.ticks = element_line(colour = "black", size = 0.25),
      axis.ticks.length.x = unit(0.08, "cm"),
      axis.ticks.length.y = unit(0.08, "cm"),
      legend.position = 'none', 
      legend.title = element_text(size = textsize),
      legend.key.size = unit(legendsize, "cm"),  
      legend.text = element_text(size = textsize)    )
}


for(i in names(p)[1:4]){
  
  p1[[i]] <- p1[[i]]+ theme(axis.ticks.x = element_blank() , 
                            axis.text.x = element_blank(),
                            plot.margin = unit(c(0.2, 0, 0, 0), "cm"),  
                            panel.background = element_blank(), 
                            plot.background = element_blank(),   
                            axis.title.x  = element_blank(),      
                            panel.grid = element_blank()       
  )
  
  p[[i]] <- p[[i]]+ theme(axis.ticks.x = element_blank() ,
                          axis.text.x = element_blank(),
                          plot.margin = unit(c(0.2, 0, 0, 0), "cm"),
                          panel.background = element_blank(),
                          plot.background = element_blank(),  
                          axis.title.x  = element_blank(),  
                          panel.grid = element_blank()  
  )
  
}

p1[[5]] <- p1[[5]]+theme(axis.line.x = element_line(colour="black", size=0.25) ,
                         plot.margin = unit(c(0.2, 0, 0, 0), "cm"))   
p[[5]] <- p[[5]]+theme(axis.line.x = element_line(colour="black", size=0.25)  ,
                       plot.margin = unit(c(0.2, 0, 0, 0), "cm"))    

( p1[[1]] +p[[1]] +plot_layout(widths = c(0.5, 0.7))) /
  ( p1[[2]] +p[[2]] +plot_layout(widths = c(0.5, 0.7))) /
  ( p1[[3]] +p[[3]] +plot_layout(widths = c(0.5, 0.7)))  /
  ( p1[[4]] +p[[4]] +plot_layout(widths = c(0.5, 0.7))) /
  ( p1[[5]] +p[[5]] +plot_layout(widths = c(0.5, 0.7))) 

ggsave(paste0('F2H',".pdf"),width =11.5, height = 10, units = "cm")
```

# Figure 2I/2J/2K. Number of biological samples (I), medical records (J) and questionnaires (K).
```{r I}
data1 <- as.data.frame(read_excel('BirthCohortData.xlsx',sheet=2))
data2 <- as.data.frame(read_excel('BirthCohortData.xlsx',sheet=3))
data3 <- as.data.frame(read_excel('BirthCohortData.xlsx',sheet=4))

data2$category <- factor(data2$category,levels = unique(data2$category))
data3$category <- factor(data3$category,levels = unique(data3$category))

col2 <- c("Early pregnancy"='#BCE4D8FF',"Late pregnancy"= '#46A1B8FF', "Delivery"='#2C5985FF', 
          "1-month"='#E1A663FF',"6-months"= '#CF9363FF',"1-year"= '#BF8061FF', "2-years"='#BB6A4FFF', "3-years"='#BB5137FF')
col3 <- c('Decidua'='#B9DDF1FF',  "Vaginal swab"='#AAD3EBFF' ,"Umbilical cord"='#9CC8E4FF',"Saliva"= '#8FBDDDFF',"Placental villous"= '#81B1D6FF' ,
          "Whole blood"='#77A8CDFF',
          "Fecal"='#6C9DC4FF' ,"Nasal swab"='#6192BDFF',"Throat swab"='#5687B4FF',"Dried blood"= '#4D7EABFF', "Breast milk" ='#4579A2FF',
          "White blood cells"='#3D6A97FF' ,"Red blood cells"='#33608DFF' ,"Plasma" ='#2A5783FF' )

pi1 <- ggplot(data1,aes(x=reorder(type,-rowsum),y=((rowsum)),fill=type))+
  geom_bar(stat = 'identity',width = 0.7) +
  scale_y_break(breaks = c(12000,30000),space = 0.2,scales = 0.4,expand = c(0,0))+
  labs(x='',y='')+
  scale_fill_manual(values=col3)+
  theme(
    axis.title.x = element_text(size = xytitle, face = 'bold'),
    axis.text.x = element_text(size = textsize, angle = anglenum, vjust = vj, hjust = hj),
    axis.title.y = element_text(size = xytitle, face = 'bold'),
    axis.text.y = element_text(size = textsize),
    plot.title = element_text(size = titlesize),
    plot.subtitle = element_text(size = textsize),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_rect(fill = NA, colour = NA),
    legend.background = element_rect(fill = NA, colour = NA),
    
    axis.line.x = element_line( colour = "black",size = 0.25),
    axis.line.y = element_line(colour = "black",size = 0.25),
    axis.ticks = element_line(colour = "black", size = 0.25),
    axis.ticks.length.x = unit(0.08, "cm"),
    axis.ticks.length.y = unit(0.08, "cm"),
    legend.position = 'none', 
    legend.title = element_text(size = textsize),
    legend.key.size = unit(legendsize, "cm"),  
    legend.text = element_text(size = textsize)    )
pi1

pi2 <- ggplot(data2,aes(x=category,y=(rowsum),fill=category))+
  geom_bar(stat = 'identity',width = 0.7) +
  scale_y_break(breaks = c(9000,25000),space = 0.2,scales = 0.4,expand = c(0,0))+
  labs(x='',y='')+
  scale_fill_manual(values=col2)+
  theme(
    axis.title.x = element_text(size = xytitle, face = 'bold'),
    axis.text.x = element_text(size = textsize, angle = anglenum, vjust = vj, hjust = hj),
    axis.title.y = element_text(size = xytitle, face = 'bold'),
    axis.text.y = element_text(size = textsize),
    plot.title = element_text(size = titlesize),
    plot.subtitle = element_text(size = textsize),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_rect(fill = NA, colour = NA),
    legend.background = element_rect(fill = NA, colour = NA),
    
    axis.line.x = element_line( colour = "black",size = 0.25),
    axis.line.y = element_line(colour = "black",size = 0.25),
    axis.ticks = element_line(colour = "black", size = 0.25),
    axis.ticks.length.x = unit(0.08, "cm"),
    axis.ticks.length.y = unit(0.08, "cm"),
    legend.position = 'none', 
    legend.title = element_text(size = textsize),
    legend.key.size = unit(legendsize, "cm"),  
    legend.text = element_text(size = textsize)    )
pi2  

pi3 <- ggplot(data3,aes(x=`category`,y=(rowsum),fill=category))+
  geom_bar(stat = 'identity',width = 0.7) +
  scale_y_break(breaks = c(7500,30000),space = 0.2,scales = 0.4,expand = c(0,0))+
  labs(x='',y='')+
  scale_fill_manual(values=col2)+
  theme(
    axis.title.x = element_text(size = xytitle, face = 'bold'),
    axis.text.x = element_text(size = textsize, angle = anglenum, vjust = vj, hjust = hj),
    axis.title.y = element_text(size = xytitle, face = 'bold'),
    axis.text.y = element_text(size = textsize),
    plot.title = element_text(size = titlesize),
    plot.subtitle = element_text(size = textsize),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_rect(fill = NA, colour = NA),
    legend.background = element_rect(fill = NA, colour = NA),
    
    axis.line.x = element_line( colour = "black",size = 0.25),
    axis.line.y = element_line(colour = "black",size = 0.25),
    axis.ticks = element_line(colour = "black", size = 0.25),
    axis.ticks.length.x = unit(0.08, "cm"),
    axis.ticks.length.y = unit(0.08, "cm"),
    legend.position = 'none', 
    legend.title = element_text(size = textsize),
    legend.key.size = unit(legendsize, "cm"),  
    legend.text = element_text(size = textsize)    )
pi3

ggsave(paste0('F2I',".pdf"),pi1,width =0.6896552*14, height = 5, units = "cm")
ggsave(paste0('F2J',".pdf"),pi2,width =0.6896552*8, height = 5, units = "cm")
ggsave(paste0('F2K',".pdf"),pi3,width =0.6896552*9, height = 5, units = "cm")
```


